---
title: "Olga Mierzwa-Sulima's CV"
author: Olga Mierzwa-Sulima
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that are inserted for placement at the end
links <- c()

source('parsing_functions.R') # Functions for building sections from CSV data
source('common_variables.R')  # Small variables for non-csv data such as intro text

# Load csv with position info
position_data <- read_csv('positions.csv')
```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-envelope"></i> olga.mierzwa@gmail.com
- <i class="fa fa-twitter"></i> olga_mie
- <i class="fa fa-github"></i> github.com/olgamie
- <i class="fa fa-link"></i> [olgamie.github.io](http://olgamie.github.io/)
- <i class="fa fa-phone"></i> +48 607 878 318

```{r}
# When in export mode the little dots are unaligned, so fix that.
if(!PDF_EXPORT){
cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/olgamie/cv/raw/master/sulima_cv.pdf)")
}
```



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
build_skill_bars(skills)
```

Main
================================================================================

Olga Mierzwa-Sulima {#title}
--------------------------------------------------------------------------------


```{r}
cat(sanitize_links(intro_text))
```




Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside_info
I have been working at consultancies that valued both technical and client-facing skills.<br> I like environments that offer learning opportunities.
:::

```{r}
print_section(position_data, 'industry_positions')
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```

<br>
<br>

Selected Data Science Talks {data-icon=chart-line}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'data_science_talks')
```

::: aside
A complete list of talks and workshops <br> I gave is available on my [blog](https://olgamie.github.io/about/)
:::

Community {data-icon=hands-helping}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'community')
```


```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


